---
title: "P8105 HW1 (pmd2137)"
output: html_notebook
---
## Problem 0

## Problem 1
```{r}
data("penguins", package = "palmerpenguins")
#summary(penguins)
```

Dataset contains data about 344 penguins.The following 8 variables are captured in the dataset and have the type indicated in parenthesis: 

    1. species (factor): Adelie = 152; Chinstrap = 68; Gentoo = 124
    2. island (factor): Biscoe = 168; Dream = 124; Torgersen = 52
    3. bill_length_mm (double): mean = 43.92 mm
    4. bill_depth_mm (double): mean = 17.5 mm
    5. flipper_length_mm (integer): mean = 200.9 mm ***
    6. body_mass_g (integer): mean = 4202 grams
    7. sex (factor): male = 165; female = 168; NA = 11
    8. year (integer): range = 2007 - 2009

```{r}
library(ggplot2)

#flipper_length_mm (y) vs bill_length_mm (x)
plot_1 <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("prob_1_plot.jpg", plot = plot_1)

plot_1
```

## Problem 2

```{r}

```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

